P.berghei pir analysis

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_CalculateTPM.Rmd
Fix consolidated similar stages and gam marker plot ordering

lapply(experiment_id, 
       function(experiment_name){
         tpm_data <- select(berghei_tpm, matches(experiment_name))
         if(ncol(tpm_data) > 3){
           dists = dist(t(tpm_data))
           par(cex=0.7)
           p <- ggdendrogram(hclust(dists)) +
             ggtitle(experiment_name)
           ggsave(filename = paste0('thesis_chapter3_figure_hclust_', 
                                    experiment_name, 
                                    '.png'),
                  plot = p,
                  path = 'plots')
           return(p)
         }
       }
)
```

@@

#Combine all Liver samples 4h or before into LiverPre4h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(2|4)h_[[:digit:]]+',
                             replacement = 'Liv.pre4h')
#Combine all Liver samples 48h or onwards into LiverPost48h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(4[8-9]|[5-9][0-9])h_[[:digit:]]+',
                             replacement = 'Liv.post48h')
#Combine all blood meal samples 3h or before into BldMlPre3h
col_stage <- str_replace_all(col_stage,
                             pattern = '(1h|3h)_[[:digit:]]+', 
                             replacement = 'Pre3h')
#Uniquify the name names
col_stage[grep(col_stage, 
               perl = TRUE,
               invert = TRUE,
               pattern = '_[[:digit:]]{1,}$')] <- uniquify(col_stage[grep(col_stage, 
                                                                          perl = TRUE,
                                                                          invert = TRUE,
                                                                          pattern = '_[[:digit:]]{1,}$')]) 
```

>>>>

lapply(experiment_id, 
       function(experiment_name){
         tpm_data <- select(berghei_tpm, matches(experiment_name))
         if(ncol(tpm_data) > 4){ 
           #No point doing hclusts for any of the expts with under four samples
           dists = dist(t(tpm_data))
           par(cex=0.7)
           p <- ggdendrogram(hclust(dists)) +
             ggtitle(experiment_name)
           ggsave(filename = paste0('thesis_chapter3_figure_hclust_', 
                                    experiment_name, 
                                    '.png'),
                  plot = p,
                  path = 'plots')
           return(p)
         }
       }
)
```

@@

#Combine all Liver samples 4h or before into LiverPre4h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(2|4)h_[[:digit:]]+',
                             replacement = 'Liv.pre4h')
#Combine all Liver samples 48h or onwards into LiverPost48h
col_stage <- str_replace_all(col_stage,
                             pattern = 'Liv\\.(4[8-9]|[5-9][0-9])h_[[:digit:]]+',
                             replacement = 'Liv.post48h')
#Combine all blood meal samples 3h or before into BldMlPre3h
col_stage <- str_replace_all(col_stage,
                             pattern = '(1h|3h)_[[:digit:]]+', 
                             replacement = 'Pre3h')
#Uniquify the name names
col_stage[grep(col_stage, 
               perl = TRUE,
               invert = TRUE,
               pattern = '_[[:digit:]]{1,}$')] <- uniquify(col_stage[grep(col_stage, 
                                                                          perl = TRUE,
                                                                          invert = TRUE,
                                                                          pattern = '_[[:digit:]]{1,}$')])

colnames(berghei_tpm) <- col_stage
```

### 2021-09-07 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
Fix consolidated similar stages and gam marker plot ordering

tpm_data_line$stage <- factor(tpm_data_line$stage, 
                             levels = ordering(tpm_data_line$stage,
                                               order_vector))

@@

(
  y <- ggplot(data = tpm_data_line, 
              aes(x = stage, 
                  y = total_tpm_median, 
                  fill = experiment, 
                  group = experiment)) +
    geom_bar(position = position_dodge2(preserve = 'single'),
             stat = 'identity') +
    scale_fill_manual(values = c(cbPalette, 'red', 'purple')[1:(length(unique(tpm_data_line$experiment)))]) +
    geom_errorbar(aes(x = stage,
                      ymax = total_tpm_max, 
                      ymin = total_tpm_min),
                  position = position_dodge2(preserve = 'single'),
                  size = 0.25) +
    scale_y_continuous(breaks = max_tpm) +
    theme_classic() +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_text(angle = 90, 
                                   size = 6, 
                                   vjust = 0.5),
          axis.text.y = element_text(size = 5),
          axis.title.y = element_text(size = 8),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 5),
          legend.key.size = unit(3,'mm'),
          legend.key.width = unit(2,'mm')) +
    scale_size(name = 'Number of genes detected over threshold', 
               range = c(0,3)) +
    ylab(
      bquote('total '~italic(.('pir'))~' TPM')
    ) +
    facet_wrap_custom(~Geneid, 
                      scales = 'free_y',
                      scale_overrides = list(
                        scale_override(3, scale_y_continuous(breaks = seq(0,650,length.out = 11))),
                        scale_override(2, scale_y_continuous(breaks = seq(0,900,length.out = 11))),
                        scale_override(1, scale_y_continuous(breaks = seq(0,310,length.out = 11)))
                      )) +
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)
)
#Could also use functions from a package called 'lemon' to add the lines to the top two facets.
```

@@

g <- ggplot(gene_expression_df,
       aes(x = pir_gene,
           y = log2(1+med_tpm))) +
  xlab('Gene group')+
  ylab('l0g(Median TPM + 1)')+
  # geom_violin()+
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               # binwidth = 1,
               # dotsize = 2,
               method = 'dotdensity') +
  geom_path(aes(group = stage,
                col = stage)) +
  theme_classic() +
  theme(
    legend.text = element_text(size = 9),
    legend.key.size = unit(4, 'mm')
  )

>>>>

tpm_data_line$stage <- factor(tpm_data_line$stage, 
                             levels = ordering(tpm_data_line$stage,
                                               r_order_vector))

@@

(
  y <- ggplot(data = tpm_data_line, 
              aes(x = stage, 
                  y = total_tpm_median, 
                  fill = experiment, 
                  group = experiment)) +
    geom_bar(position = position_dodge2(preserve = 'single'),
             stat = 'identity') +
    scale_fill_manual(values = c(cbPalette, 'red', 'purple')[1:(length(unique(tpm_data_line$experiment)))]) +
    geom_errorbar(aes(x = stage,
                      ymax = total_tpm_max, 
                      ymin = total_tpm_min),
                  position = position_dodge2(preserve = 'single'),
                  size = 0.25) +
    scale_y_continuous(breaks = max_tpm) +
    theme_classic() +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_text(angle = 90, 
                                   size = 6, 
                                   vjust = 0.5),
          axis.text.y = element_text(size = 5),
          axis.title.y = element_text(size = 8),
          legend.title = element_text(size = 7),
          legend.text = element_text(size = 5),
          legend.key.size = unit(3,'mm'),
          legend.key.width = unit(2,'mm')) +
    scale_size(name = 'Number of genes detected over threshold', 
               range = c(0,3)) +
    ylab(
      bquote('total '~italic(.('pir'))~' TPM')
    ) +
    facet_wrap_custom(~Geneid, 
                      scales = 'free_y',
                      scale_overrides = list(
                        scale_override(3, scale_y_continuous(breaks = seq(0,650,length.out = 11))),
                        scale_override(2, scale_y_continuous(breaks = seq(0,900,length.out = 11))),
                        scale_override(1, scale_y_continuous(breaks = seq(0,310,length.out = 11)))
                      )) +
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)
)
#Could also use functions from a package called 'lemon' to add the lines to the top two facets.

ggsave('plots/thesis_chapter3_figure_gametocyteMarkers.png',
       width = 7,
       height = 5,
       units = "in",
       y)
```

@@

g <- ggplot(gene_expression_df,
       aes(x = pir_gene,
           y = log2(1+med_tpm))) +
  xlab('Gene group')+
  ylab('log(Median TPM + 1)')+
  # geom_violin()+
  geom_dotplot(binaxis = 'y',
               stackdir = 'center',
               # binwidth = 1,
               # dotsize = 2,
               method = 'dotdensity') +
  geom_path(aes(group = stage,
                col = stage)) +
  theme_classic() +
  theme(
    legend.text = element_text(size = 9),
    legend.key.size = unit(4, 'mm')
  )
